\section{Problem description}

\emph{This is the problem description, as per the customer's request.}

Social networking sites such as Facebook\cite{link:facebook} and Twitter\cite{link:twitter}
have normally been accessed  via a web browser. Lately mobile versions have become popular,
and allow access to context data such as location of users. We foresee a much greater popularity
of mobile and pervasive interfaces to social media in the coming years.

Arduino\cite{link:arduino} is a platform that allows software to be written in order to construct
hardware prototypes. In this task the students will develop an Arduino-based interface to Facebook.
The information from Facebook will be made available on Arduino displays and the user can interact
with Facebook through Arduino sensors and actuators.

In case Facebook data access shows to be difficult, the students will use Shindig\cite{link:shinding} which 
is an open source implementation of OpenSocial\cite{link:opensocial} APIs. The service specification is developed
in the European project SOCIETIES in collaboration with European partners. The students are however expected to
innovate and come up with new concepts, user interfaces, and service organization.

\section{The context}
In the past few years, social networks have become more and more popular, continuously increasing their user-base.
The project task was to design and develop an open source Android\cite{link:android} framework for allowing quick
and flexible development of wireless Tangible User Interfaces (TUI) for social networks using Arduino.
The product has served both as a proof-of-concept and as a starting point for future software projects.

\section{The customer}
Our customer was SINTEF, represented by Mr. Babak A. Farshchian.

SINTEF is the largest independent research organization in Scandinavia\cite{link:sintef}.
It is an independent, non-commercial organization with their head office in Trondheim.
They have approximately 2100 employees, mainly in Trondheim and Oslo.

\section{The team}
The team consisted of six students from NTNU and one exchange student.
About half of the members have worked together on previous projects and thus shared
some teamwork skills and experiences. None of the team members had worked for a customer before.

\subsection{Team members}

\begin{itemize}
\item{\anders}\newline
Third year Informatics student at NTNU. Experience with the programming languages Java,
C and C++. Also experience with Arduinos, AVRs and some basic electronics knowledge.

\item{\henrik}\newline
Third year student at NTNU. Main language Java, basic knowledge in 3D and electronic circuits.

\item{\johan}\newline
Third year student at NTNU. Experience with the programming languages Java, C, C++  and
Basic. Worked with AVR micro-controllers in other projects and courses.

\item{\asbjorn}\newline
Second year student on bachelor in computer science at NTNU. Has previously had one year of
introductory psychology which is to be included in the bachelor in computer science.
Experience with Java.

\item{\emanuele}\newline
Third year Computer Science exchange student from Tor Vergata University, Rome.
Experience with Java, C and C++ programming, basic electronic notions.

\item{\jonas}\newline
Third year student at NTNU. Experience with Java, Python, Lua, PHP, and web standards such as HTML, 
CSS and Javascript. Previously worked with media production and sound engineering.

\item{\bjornar}\newline
Third year Informatics student at NTNU. Experience with programming in Java, C and C++.
Previously worked with electronics and have basic knowledge about AVR micro-controllers through
own projects.
\end{itemize}

\section{Definitions}

Here we introduce a list of the terms used in this document with a short explanation of their meaning.

\begin{description}

\item[Android:]
	An operating system based on Linux primarily for mobile devices. It features a software stack, and applications are written in the Java language. Android is made by Google and the Open Handset Alliance.
\item[Android-Arduino applications:]
	With this term we refer to Android applications used to control the behavior of Arduino-based tangible user interfaces.
\item[Apache:]
	A software foundation focused on open source and community driven software.
\item[Arduino:]
	Arduino is a tool for making computers that can sense and control more of the physical world than your
	desktop computer. It's an open-source physical computing platform based on a simple micro-controller board, and a development
	environment for writing software for the board. 
\item[Facebook:]
	Facebook is the biggest social network. It is also the network our libraries primarily focus on.
\item[IPC:]
	Remote Method Invocation in Java (RMI) or Remote Procedure Call in C (RPC) are two implementations of inter-process communication (IPC).
	This allows two different computer programs (possibly on two entierly different systems or platforms) to execute code in their respective
	address space.
\item[JSON:]
	Acronym for Javascript object notation. It is a lightweight data interchange format,
	used in most social networks.
\item[MVC:]
	Acronym for the Model, View, Controller pattern. It's a design pattern used to abstract the data model, logic and presentation.
\item[OpenSocial:]
	OpenSocial is an open source standard by Google for a set of API. It's aim is to
	provide a common runtime environment for web applications within different social networks. It is supported by networks
	such as Orkut, MySpace, LinkedIn and many more, except Facebook and Twitter.
\item[oSNAP:]
	The code name for this project. Acronym for Open Social Network Arduino Platform.
\item[Product:]
	This project's deliverables: a set of prototypes and Android applications and libraries.
\item[Prototype:]
	An Arduino board, running a custom firmware, acting as a tangible user interface.
\item[REST:]
	A software architecture for distributed systems. Software that complies with REST constrains is called RESTful.
\item[RPC:]
	See IPC.
\item[RMI:]
	See IPC.
\item[Shield:]
	An Arduino chip (or module) one puts on top of the main board to extends the arduino's feature set.
\item[Shindig:]
	Shindig is Apache's implementation of the OpenSocial standard.
\item[Social service/applications:]
	With this term we refer to Android applications, used to fetch data from a social network.
\item[TUI:]
	Acronym for tangible user interfaces.
\item[Twitter:]
	World's biggest micro-blogging network.
	
\end{description}
