%\newcommand{\Date}{}

\section{Date: 20/01/2012}

\textbf{Participants:} Everyone

\textbf{Agenda}

\begin{itemize}
	\item First meeting, 
	\item Contact the client
	\item Contacted the client
	\begin{itemize}\item First meeting at Friday 27/01 at 14:00 \end{itemize}


	\item Send mail to the client with phone numbers/names

	\item Checking free slots in schedule when we can have meetings
	\begin{itemize}
		\item (Monday 12:15 and out)
		\item (Entire Wednesday)
		\item (Friday 14:15 and out)
	\end{itemize}
\end{itemize}

\textbf{To do to next meeting:}

Check solutions for connecting Facebook and Arduino\newline
$Facebook -> openSocial (Java) -> C/Arduino IDE -> Chipset$

\begin{itemize}
	\item Everyone
	\begin{itemize}
		\item BrainStorm
		\item Make some notes/schemes.
	\end{itemize}

	\item Henrik
	\begin{itemize}
		\item Read on OpenSocial
	\end{itemize}

	\item Jonas
	\begin{itemize}
		\item Setup GIT, Mailing list, examine OpenSocial and Shindig
	\end{itemize}

	\item Emanuele
	\begin{itemize}
		\item Find available Facebook APIs, document on Open Social, Apache Shindig..
	\end{itemize}

	\item Asbjørn
	\begin{itemize}
		\item Read on Arduino
	\end{itemize}

	\item Anders and Bjørnar
	\begin{itemize}
		\item Connect arduino to java
	\end{itemize}

	\item Johan
	\begin{itemize}
		\item OpenSocial, Java -> Arduino
		\item Send two mail
		\item To SINTEF
		\item To reception to book room Friday 4th floor at 14:15 every week
	\end{itemize}
\end{itemize}


\textbf{Next meeting:}

Monday 23/01 GreenHouse\newline
Discuss brainstorm/possiblities\newline
Get a meeting room at Friday at 14, to meet with the client


\section{Date: 23/01/2012}

\textbf{Participants:} Everyone

\textbf{Agenda}

\begin{itemize}
	\item We will probably use the Java Facebook API library restFB. 
	\item Shared some ideas. Discussed a little bit on the development process to use.
	\item Will probably adopt Scrum as development process, given the iterative nature of our work schedule and of the meetings with customer.
	\item Realized a proof of concept consisting in a led turned on by Arduino if there is any unread notification on Facebook.
\end{itemize}

\begin{itemize}
	\item Henrik
	\begin{itemize}
		\item Read on OpenSocial
		\item Results
		\begin{itemize}
			\item Disregard Open Social
			\item Idea: Facebook game: Torture instrument at NTNU
		\end{itemize}
	\end{itemize}

	\item Jonas
	\begin{itemize}
		\item Setup GIT, Mailing list, examine OpenSocial and Shindig
		\item Results
		\begin{itemize}
			\item Git and mailinglist up
		\end{itemize}
	\end{itemize}

	\item Emanuele
	\begin{itemize}
		\item Read on available Facebook and other social networks Java API.
		\item Results
		\begin{itemize}
			\item Read the Facebook developers pages (Facebook Graph API, Access tokens..)
and Open Social documentation. It turned out Facebook does not implement the Open Social standard. restFB, a simple, flexible, actively developed and permissively licensed (MIT) Java Facebook API was found and used to code a small program that checks for unread notifications.
		\end{itemize}
	\end{itemize}

	\item Asbjørn
	\begin{itemize}
		\item Read on Arduino
		\item Results
		\begin{itemize}
			\item Idea: Handshake friend request
			\item Idea: Camera takes profile picture.
		\end{itemize}
	\end{itemize}

	\item Anders and Bjørnar
	\begin{itemize}
		\item Connect Arduino to java
		\item Results
		\begin{itemize}
			\item Success!
		\end{itemize}
	\end{itemize}

	\item Johan
	\begin{itemize}
		\item OpenSocial, Java -> Arduino
		\item Send two mail
		\item To SINTEF
		\item To reception to book room Friday 4th floor at 14:15 every week
		\item Results
		\begin{itemize}
			\item Acquired room: 236 it-syd. Every Friday from 14:00 to 17:00
			\item Mail sent to client to meet at room next Friday.
		\end{itemize}
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item Henrik
	\begin{itemize}
		\item Create idea presentations for Client.
	\end{itemize}

	\item Jonas and Johan
	\begin{itemize}
		\item Collaboration tools
	\end{itemize}

	\item Emanuele
	\begin{itemize}
		\item Try to find an alternative to polling Facebook. (A callback mechanism?)
	\end{itemize}

	\item Asbjørn
	\begin{itemize}
		\item Documentation research
	\end{itemize}

	\item Anders and Bjørnar
	\begin{itemize}
		\item Program library for serial Arduino to Java communication
	\end{itemize}
\end{itemize}

\textbf{Next meeting:}

Wednesday 25/01 GreenHouse\newline
Prepare presentations\newline
Implement collaboration tools
