\subsection{Participants:}
 Everyone present

Meeting started at 14.15


\subsection{Agenda}
Meeting with the customer to show the working prototype according to the specs he had given us.
Talk about issues we had encountered and how they can be fixed.
Presentation of the framework by Henrik.
Get feedback from the customer about what we have done this far, and what he wants us to do next.


\subsection{Additional Information}
Meetings are now moved to 14.15 every Friday, instead of 14.00.
During this meeting the customer had a clearer plan about what the end product should be, and how to get there. This will lead to a rework of the design/plan for this project, but we have a smaller and more specific task to be carried out. This includes making an app/service for the Android OS that uses intents[1] to communicate with other apps on the Android OS.
The use of a custom bootloader for the Arduino is postponed until further notice.


\subsection{ To do for next meeting}
Everyone have to read up on Android Intents and get a basic grasp of the functionality of the Open Social API.
Finish the preliminary report that is due for Monday.
Read up on NFC, find a way we can use it to for example establish connection between a phone and an Arduino device.


\subsection{ To do for next meeting with the customer}
Find out how to separate and use the intents
Make an API to communicate with Android apps through intents, and send this information using bluetooth to an Arduino device.
The API should be able to support different modules(t-shirt, mailbox, etc)
If we have time for it, simulate the use of QR codes to download an app to the phone.
Write a list of what we have to order to make the product/prototype.

Intents can be used to signal to the Android system that a certain event has occurred. Other components in Android can register to this event and will get notified.