Participants: Anders, Bjoernar, Henrik and Johan

Meeting started at 14.15

Agenda
Get feedback on the preliminary report.

Additional Information
Meetings with the student assistant will be held every two weeks, if we are not at P15, we have to remember to notify him. 


Team member roles have to be assigned, each member should also write something about themselves (background, experience/knowledge, what work you have done earlier and stuff like that)


Add more information about why we have chosen Scrum, write something about other development models (Waterfall, Spiral, Agile, Iterative etc) and why we didnt choose to use them. Should also include more about how we have adapted Scrum to our needs.


The status reports should be renamed to the sprints?

Alternate/existing solutions can be put under the pre-studies chapter.


The report should be restructured a bit. See the mail for additional info.


1. Introduction
1.1 The context
1.2 The Customer

2. Process Management
2.1 Process methodologies
2.2 Our choice
2.3 The team
2.4 Project management tools
2.5 Risk analysis and migration strategies
2.6 Schedule (Gant Diagrams, WBS etc)


3. Pre-study
3.1 Communication resources
3.2 Time resources
3.3 Existing solutions
3.4 Software and hardware development tools
3.5 Add more pre-study

4. Requirements
4.1 Functional requirements
4.2 Non functional requirements

5. Architecture Design
5.1 First approach
5.2 Revised approach
5.3 Architecture diagram
5.4 Use cases

System testing, results etc..