\subsection{Participants}
Everyone

\subsection{Agenda}
We will probably use the Java Facebook API library restFB. 
Shared some ideas. Discussed a little bit on the development process to use.
Will probably adopt Scrum as development process, given the iterative nature of our work schedule and of the meetings with customer.
Realized a proof of concept consisting of a LED turned on by the Arduino, if there is any unread notifications on Facebook.

{\bf Henrik: } \newline
\begin{itemize}
\item Read on OpenSocial
\end{itemize}

Results
\begin{itemize}
\item Disregard Open Social
\item Idea: Facebook game: Torture instrument at NTNU
\end{itemize}

{\bf Jonas:} \newline
\begin{itemize}
\item Setup GIT, Mailing list, examine OpenSocial and Shindig
\end{itemize}

Results
\begin{itemize}
\item Git and mailing-list up
\end{itemize}

{\bf Emanuele: } \newline
\begin{itemize}
\item Read on available Facebook and other social networks Java API.
\end{itemize}

Results
\begin{itemize}
\item Read the Facebook developers pages (Facebook Graph API, access tokens..)
and Open Social documentation. 
\item It turned out Facebook does not implement the Open Social standard. restFB, a simple, flexible, actively developed and permissively licensed (MIT) Java Facebook API was found and used to code a small program that checks for unread notifications.
\end{itemize}

{\bf Asbjørn: } \newline
\begin{itemize}
\item Read on Arduino
\end{itemize}

Results
\begin{itemize}
\item Idea: Handshake friend request
\item Idea: Camera takes profile picture.
\end{itemize}


{\bf Anders and Bjørnar: } \newline
\begin{itemize}
\item Connect Arduino to Java
\end{itemize}

Results
\begin{itemize}
\item Success!
\end{itemize}

{\bf Johan: } \newline
\begin{itemize}
\item OpenSocial, Java -> Arduino
\item Send two mail
\item To SINTEF
\item To reception to book room Friday 4th floor at 14:15 every week
\end{itemize}

Results
\begin{itemize}
\item Acquired room: 236 it-syd. Every Friday from 14:00 to 17:00
\item Mail sent to client to meet at room next Friday.
\end{itemize}

\subsection{Next meeting}

{\bf Henrik: } \newline
Create idea presentations.

{\bf Jonas and Johan: } \newline
Collaboration tools

{\bf Emanuele: } \newline
Try to find an alternative to polling Facebook. (A callback mechanism?)

{\bf Asbjørn: } \newline
Documentation research

{\bf Anders and Bjørnar: } \newline
Program library for serial Arduino to Java communication

\subsection{Next meeting}
Wednesday 25/01 GreenHouse

Prepare presentations

Implement collaboration tools
