First weeks status report where major directional decisions will be explained.

\subsection{Progress summary}
The starting weeks work was mainly focused on identifying the specifics of our task and for every group member to start individual research into possibilities in Arduino, Facebook APIs, other social network APIs and then reporting it back to the group at our meetings. Together we tried to find good concepts for the Tangible User Interface(TUI) product that we was going to make. We had a meeting with the customer on the friday where we discussed our concepts. In this meeting the customer voiced wishes for the project to go in a more general direction than focusing on specific tangible end products. We was going to make a framework where creating products with an Arduino chip was lessened in complexity both for the developer and the end user.
We also got Arduino products(Bluetooth module etc) from Simone Mora from IDI.

\subsection{Open / closed problems}
The direction the project should pursue in regards to the TUI and platform choice became clear on  the meeting with the customer.
How well the Arduino chip could handle wireless connections(Bluetooth, WiFi or Zigby) is an open problem.

\subsection{ Planned work for next period}
In the meeting with the customer we decided on a task for the next period. If we could show that the Arduino could be linked with an Android and/or PC through a wireless connection we could further refine the requirements and goals of the project. 

\subsection{Updated risks analysis}
Wireless connectivity; if the Arduino chip addon modules(called SHIELDS) for Bluetooth etc. was too hard to implement we would have to reconsider wireless connectivity. We set the get "wireless to work" deadline to be one month. Otherwise we would have to use only cabled connections and that would be clumsy on a lot of cool concepts.
 Likelihood: 4 Impact: 6 Importance: 24